Analysis of the properties of probabilistic models in learning problems with an expert\thanks{The reported study was funded by Russian Foundation for Basic Research according to the research projects 20-37-90050, 19-07-01155 and National Technological Initiative project 13/1251/2018.}

### 2022-01-30 paper/Grabovoy2022ExpertLearningAIT/BliendedManuscript.tex
fix

\title{Analysis of the properties of probabilistic models in learning problems with an expert\thanks{The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.}
}
\subtitle{}

@@

\section{Acknowledgments}
\label{sec:7}
The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

>>>>

\title{Analysis of the properties of probabilistic models in learning problems with an expert\thanks{The reported study was funded by Russian Foundation for Basic Research according to the research projects 20-37-90050, 19-07-01155 and National Technological Initiative project 13/1251/2018.}
}
\subtitle{}

@@

\begin{acknowledgements}
The reported study was funded by Russian Foundation for Basic Research according to the research projects 20-37-90050, 19-07-01155 and National Technological Initiative project 13/1251/2018.
\end{acknowledgements}

### 2022-01-30 paper/Grabovoy2022ExpertLearningAIT/Manuscript.tex
fix

\section{Acknowledgments}
\label{sec:7}
The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.

>>>>

\begin{acknowledgements}
The reported study was funded by Russian Foundation for Basic Research according to the research projects 20-37-90050, 19-07-01155 and National Technological Initiative project 13/1251/2018.
\end{acknowledgements}
